---
title: "Simulation5.1_GAM"
author: "Maja Gledić"
date: "2025-06-28"
output: pdf_document
---

This is the code for performing the cross-validation where the nuisance-models 
are defined as a generalized additive propensity score models.
Therefore, the cross-validation procedure is the same as for the baseline model, 
with the only difference being the type of nuisance models. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# list of required packages
packages_needed <- c("dplyr", "ggplot2", "pbapply", "mgcv")

# install any missing packages and load libraries
for (pkg in packages_needed) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  } else {
    library(pkg, character.only = TRUE)
  }
}
```


# Generate Data
```{r data generation function}
# create function that generates data
sim_data <- function(n, seed) {
  set.seed(seed)
  
  x1 <- rnorm(n, mean = 0, sd = 1)                      
  x2 <- 0.6*x1 + rnorm(n, mean = 0, sd = 0.5)           
  x3 <- rbinom(n, 1, 0.5)                               
  x4 <- sample(1:3, n, replace = TRUE)                  
  x5 <- 0.4*x1 + 0.3*x2 + rnorm(n, mean = 0, sd = 0.5)  
  x6 <- 0.5*x5 - 0.2*x3 + rnorm(n, mean = 0, sd = 0.5) 
  
  # probability of treatment assignment based on all observed confounders
  # positivity assumption
  prob_a <- plogis(-0.175 + 0.1*x1 + 0.3*x2 + 0.2*x3 - 0.01*(x4 == 2) + 0.02*x5 - 0.3*x6)
  a <- rbinom(n, 1, prob_a)   # (1 = treated, 0 = untreated)
  
    
  # create relationship between observed confounders and conterfactual outcomes
  # these denote the potential outcomes for each individual 
  # under both treatment conditions
  # homogenous treatment assignment where covariate effect is the same
  # only difference is treatment effect (last term)
  y_a1 <- rbinom(n, 1, plogis(-1.2 + 0.005*x1 + 0.003*x2^2 + 0.004*x5 - 0.002*x6 + 0.002*x3^3 - 0.004*(x4 == 3) + 0.0025*1))  # treated
  y_a0 <- rbinom(n, 1, plogis(-1.2 + 0.005*x1 + 0.003*x2^2 + 0.004*x5 - 0.002*x6 + 0.002*x3^3 - 0.004*(x4 == 3) + 0.0025*0))  # untreated
  
  # observed outcome based on actual treatment
  # consistency assumption
  y_obs <- ifelse(a == 1, y_a1, y_a0)
  
  df <- data.frame(X1 = x1, X2 = x2, X3 = as.factor(x3), 
                   X4 = as.factor(x4), X5 = x5, X6 = x6, 
                   A = as.factor(a), 
                   Y_a0 = as.factor(y_a0),
                   Y_a1 = as.factor(y_a1),
                   Y_obs = as.factor(y_obs))
  
  return(df)
}
```

# Cross-validation Procedure
```{r cross-validation procedure, warning=FALSE}

# create function to run 5-fold cross-validation
# define the function to run 'r' replications for a given sample size 'n',
# with 'k' number of folds


cv_manual <- function(n, r, k_folds = 5) {
  
  # run simulated data
  df <- sim_data(n, seed = 123 + r)
  # partition data into 5 folds
  folds <- cut(sample(nrow(df)), breaks = k_folds, labels = FALSE)
      
  # initialise storage of Brier scores across 5 folds
  true_brier_A0 <- numeric(k_folds)
  true_brier_A1 <- numeric(k_folds)
  est_brier1_A0 <- numeric(k_folds)
  est_brier1_A1 <- numeric(k_folds)
  est_brier2_A0 <- numeric(k_folds)
  est_brier2_A1 <- numeric(k_folds)
  est_brier3_A0 <- numeric(k_folds)
  est_brier3_A1 <- numeric(k_folds)
  est_brier4_A0 <- numeric(k_folds)
  est_brier4_A1 <- numeric(k_folds)
                  
# for loop for cross-validation
  for (i in 1:k_folds){

    # ----------------
    # PREDICTION MODEL
    # ----------------
    
    # assign train and validation sets such that the split is 80/20
    train <- df[folds != i, ]
    test <- df[folds == i, ]
    
    # NUISANCE MODEL 1: generalized additive propensity score model
    # develop propensity score model from train data and determine weights
    ps_null <- gam(A ~ s(X1) + s(X2) + X3 + X4 + s(X5)+ s(X6), 
               data = train, family = "binomial")
    # estimate propensity scores for the training set
    train$ps_null <- predict(ps_null, type = "response")
    # get inverse probability weights for the training set
    train$weights_null <- ifelse(train$A == 1, 1/train$ps_null, 1/(1-train$ps_null))   
    
    # create weighted prediction model by including the training set weights
    # define prediction model as logistic regression model
    model_null <- glm(Y_obs ~ A + X1 + X2 + X3 + X4 + X5 + X6, data = train, 
                      family = "binomial", weights = train$weights_null)
    
    # the test set will be used for making predictions
    # need to create scenarios so that for all observations A={0,1}
    # create two test sets and make A={0,1} for all
    test_A0 <- test
    test_A0$A <- as.factor(0)
    test_A1 <- test 
    test_A1$A <- as.factor(1)
    
    # get predictions from test sets (a=0, a=1) and attach to original test set
    # each individual should have two predictions (predicted counterfactual outcomes)
    test$predsA0 <- predict(model_null, newdata = test_A0, type = "response")  
    test$predsA1 <- predict(model_null, newdata = test_A1, type = "response") 
    
    # ----------------
    # TRUE BRIER SCORE
    # ----------------
    
    # extract true counterfactuals from test set based on treatment assignment
    test_Y_a0 <- as.numeric(test$Y_a0) - 1
    test_Y_a1 <- as.numeric(test$Y_a1) - 1
    

    # evaluate performance for each iteration:
    # compare simulated counterfactuals with prediction probabilities
    # this is the estimated benchmark for counterfactual performance 

    true_brier_A0[i] <- mean((test_Y_a0 - test$predsA0)^2)   
    true_brier_A1[i] <- mean((test_Y_a1 - test$predsA1)^2)
    
    # ---------------------
    # ESTIMATED BRIER SCORE
    # ---------------------
    
    # this is the estimated counterfactual Brier score 
    # this involves implementing the four strategies 
    # for estimating NUISANCE MODEL 2 

    # extract observed outcomes - we use these for computing the Brier score
    test$Y_obs <- as.numeric(test$Y_obs) - 1

    # --------------------------------------------------
    # STRATEGY 1: develop nuisance model using FULL DATA
    # --------------------------------------------------
    
    # STEP 1: train propensity score model using full data
    ps_model1 <- gam(A ~ s(X1) + s(X2) + X3 + X4 + s(X5)+ s(X6), 
                 data = df, family = "binomial")  
    # STEP 2: estimate propensity scores for the validation set
    test$ps1 <- predict(ps_model1, newdata = test, type = "response")  
    # STEP 3: get weights for the validation set 
    test$weights1 <- ifelse(test$A == 1, 1 / test$ps1, 1 / (1 - test$ps1))        
    
    # STEP 4: compute estimated Brier scores for each iteration:
    # using observed outcomes, predicted probabilities from prediction model,
    # and weights from nuisance model 2
    est_brier1_A0[i] <- mean(test$weights1 * (test$A==0) * (test$Y_obs - test$predsA0)^2) 
    est_brier1_A1[i] <- mean(test$weights1 * (test$A==1) * (test$Y_obs - test$predsA1)^2)
  
    # -----------------------------------------------------
    # STRATEGY 2: develop nuisance model using TRAINING SET
    # -----------------------------------------------------
    
    # STEP 1: train propensity score using training set
    # Repeat steps 2-4 

    ps_model2 <- gam(A ~ s(X1) + s(X2) + X3 + X4 + s(X5)+ s(X6), 
                  data = train, family = "binomial")  
    test$ps2 <- predict(ps_model2, newdata = test, type = "response")  
    test$weights2 <- ifelse(test$A == 1, 1 / test$ps2, 1 / (1 - test$ps2))
    
    est_brier2_A0[i] <- mean(test$weights2 * (test$A==0)* (test$Y_obs - test$predsA0)^2)
    est_brier2_A1[i] <- mean(test$weights2 * (test$A==1)* (test$Y_obs - test$predsA1)^2) 
    
    # ---------------------------------------------------------
    # STRATEGY 3: develop nuisance model using validation data
    # ---------------------------------------------------------
    
    # STEP 1: train propensity score using test set
    # Repeat steps 2-4 
    ps_model3 <- gam(A ~ s(X1) + s(X2) + X3 + X4 + s(X5)+ s(X6), 
               data = test, family = "binomial") 
    test$ps3 <- predict(ps_model3, newdata = test, type = "response") 
    test$weights3 <- ifelse(test$A == 1, 1 / test$ps3, 1 / (1 - test$ps3))
    
    est_brier3_A0[i] <- mean(test$weights3 * (test$A==0) * (test$Y_obs - test$predsA0)^2) 
    est_brier3_A1[i] <- mean(test$weights3 * (test$A==1) * (test$Y_obs - test$predsA1)^2)
  
    # -------------------------------------------------------
    # STRATEGY 4: develop nuisance model using "nuisance" set
    # -------------------------------------------------------
  
    # STEP 1: split test into 2 parts - nuisance and remainder of test set
    # we partition the test set such that it is a 50/50 split
    # we split the test set instead of the training set to keep the data
    # used for the prediction model (prediction probabilities) the same
    idx <- sample(nrow(test), size = round(0.5*nrow(test)), replace = FALSE) 
    nuisance <- test[idx,]
    remaining <- test[-idx,]
    
    # STEP 2: train the propensity score using the nuisance set
    ps_model4 <- gam(A ~ s(X1, k=4) + s(X2, k=4) + X3 + X4 + s(X5, k=4)+ s(X6, k=4), 
               data = nuisance, family = "binomial") 
    
    # STEP 3: estimate propensity scores on the remaining validation set
    remaining$ps4 <- predict(ps_model4, newdata = remaining, type = "response") 
    # STEP 4: get weights for remaining test (validation) set
    remaining$weights4 <- ifelse(remaining$A == 1, 1 / remaining$ps4, 1 / (1 - remaining$ps4))

    # STEP 5: estimate Brier scores accordingly
    est_brier4_A0[i] <- mean(remaining$weights4 * (remaining$A==0) * (remaining$Y_obs - remaining$predsA0)^2)
    est_brier4_A1[i] <- mean(remaining$weights4 * (remaining$A==1) * (remaining$Y_obs - remaining$predsA1)^2)
  }
  
  # average the Brier scores across the 5-folds
  data.frame(replication = r,
            sample_size = n,  
            True_A0 = mean(true_brier_A0),
            True_A1 = mean(true_brier_A1),
            Est1_A0 = mean(est_brier1_A0),
            Est1_A1 = mean(est_brier1_A1),
            Est2_A0 = mean(est_brier2_A0),
            Est2_A1 = mean(est_brier2_A1),
            Est3_A0 = mean(est_brier3_A0),
            Est3_A1 = mean(est_brier3_A1),
            Est4_A0 = mean(est_brier4_A0),
            Est4_A1 = mean(est_brier4_A1))

}
```

```{r analysis checks}
  
# check propensity scores and weights

# mean(test$ps1)
# mean(test$ps2)
# mean(test$ps3)
# mean(as.numeric(test$A)-1)
# mean(remaining$ps4)
# mean(as.numeric(remaining$A)-1)
# 
# # distribution of propensity scores
# ggplot(data = remaining, mapping = aes(x = ps4, fill = A)) +
#   geom_histogram(bins = 10)
# 
# ggplot(data = test, mapping = aes(x = ps1, fill = A)) +
#   geom_histogram(bins = 10)
# 
# # distribution of weights
# summary(test$weights3)
# summary(remaining$weights4)

```


## Replications and Sample Sizes
```{r replicate simulation, warning=FALSE}

# set number of simulation replications
n_reps <- 100
# set various sample sizes
sample_sizes <- c(500, 1000, 1e4, 1e5)

# for loop for running cross-validation for each sample size "n_rep" times
for (n in sample_sizes) {
  
  # run cross-validation for all replications per sample size
  results_cv_list <- pblapply(1:n_reps, function(r) {
    suppressMessages(cv_manual(n = n, r = r))
  })
  
  # combine results from each replication 
  results_cv_gam <- do.call(rbind, results_cv_list)
  # save results from each sample size as .rda file
  save(results_cv_gam, file = paste0("results_GAM_", n, ".rda"))
  
  message("Finished and saved: Sample Size = ", n)
}

```

## Loading the saved data files
```{r load saved files}

sample_sizes <- c(500, 1000, 1e4, 1e5)
# load the files for each sample size
loaded_results <- lapply(sample_sizes, function(n) {
  
  file_name <- paste0("results_GAM_", n, ".rda")
  data <- get(load(file_name))
  return(data)
})

# removed Brier scores above 5 (should actually be between 0 and 1)
# this removed 8 rows
loaded_results[[1]] <- loaded_results[[1]] %>% filter(Est4_A1 <= 5)

combined_results_gam <- do.call(rbind, loaded_results)

```


# Summary
## Untreated Group

### Distribution of Brier scores
```{r distribution of Brier scores}
# subset such that we only have for a=0 
# transform into long formatlong_df0_gam <- combined_results_gam %>%
  dplyr::select(replication, sample_size, True_A0, Est1_A0, Est2_A0, Est3_A0, Est4_A0) %>%
  tidyr::pivot_longer(cols = starts_with("True_A0"):starts_with("Est4_A0"), 
               names_to = "strategy", values_to = "brier_score")

# rename to display strategy names
long_df0_gam <- long_df0_gam %>% mutate(strategy = recode(strategy,
                           "True_A0" = "True",
                           "Est1_A0" = "Full_Data",
                           "Est2_A0" = "Training_Set",
                           "Est3_A0" = "Test_Set",
                           "Est4_A0" = "Nuisance_Set")) %>%
            mutate(strategy = factor(strategy, 
                           levels = c("True","Full_Data", 
                                      "Training_Set", "Test_Set", 
                                      "Nuisance_Set")))

#-------------------------------------------------------------------------------

# Boxplot: distribution of Brier score estimates from 100 replications
boxplot0_gam <- ggplot(long_df0_gam, 
                      aes(x = strategy, y = brier_score, 
                          fill = strategy, color = strategy)) +
  
  geom_jitter(alpha = 0.5) +
  geom_boxplot(alpha = 0.7, color = "black") +
  
  labs(# title = "Distribution of Brier Scores (A=0)",
       # subtitle = "Logistic Regression Nuisance Model", 
       # caption = "Average estimates from 1000 replications",
       y = "Average Brier Score", x = "") +
  
  scale_color_manual(values = c("True" = "#F8766D",
                                "Full_Data" = "#CD9600", 
                                "Training_Set" = "#00C19A", 
                                "Test_Set" = "#00A9FF",
                                "Nuisance_Set" = "#ED68ED"), 
                     name = "Strategy") +
  
  scale_fill_manual(values = c("True" = "#F8766D",
                                "Full_Data" = "#CD9600", 
                                "Training_Set" = "#00C19A", 
                                "Test_Set" = "#00A9FF",
                                "Nuisance_Set" = "#ED68ED"), 
                    name = "Strategy") +

  theme_minimal() +
  
  theme(axis.text.x = element_blank()) +
  
  facet_wrap(~sample_size) +
  
  scale_y_continuous(limits = c(0.14, 0.26)) 


# ggsave("boxplot0_gam.png", plot = boxplot0_gam)
```


### Average Brier scores 
```{r average Brier scores}
# subset Brier scores such that we only have for a=0
results_A0 <- combined_results_gam %>% dplyr::select(replication, sample_size, 
                                 True_A0, Est1_A0, Est2_A0, Est3_A0, Est4_A0)

# compute the mean and standard deviations for each score
# across the simulation runs
summary_stats_A0 <- results_A0 %>%
  group_by(sample_size) %>%
  summarise(across(.cols = c(True_A0, Est1_A0, Est2_A0, Est3_A0, Est4_A0),
                   .fns = list(mean_brier = mean, sd_brier = sd),
                   .names = "{.col}_{.fn}"))


# transform the dataframe to separate values based on strategies 
summary_A0 <- summary_stats_A0 %>%
  tidyr::pivot_longer(
    cols = -sample_size, 
    names_to = c("strategy", "metric"), 
    names_sep = "_A0_") %>%
  tidyr::pivot_wider(names_from = metric,
                     values_from = value) %>%
  mutate(strategy = recode(strategy,
                           "True" = "True",
                           "Est1" = "Full_Data",
                           "Est2" = "Training_Set",
                           "Est3" = "Test_Set",
                           "Est4" = "Nuisance_Set")) %>%
  mutate(strategy = factor(strategy, 
                           levels = c("True","Full_Data", 
                                      "Training_Set", "Test_Set", 
                                      "Nuisance_Set")))
```


```{r plot averages}
# illustrate average Brier scores across increasing sample size
mean_briers0_gam <- ggplot(data = summary_A0, 
       mapping = aes(x = as.factor(sample_size),
                     y = mean_brier, 
                     color = strategy, 
                     shape = strategy, 
                     linetype = strategy, 
                     group = strategy)) +
  
  geom_point(size = 3) +
  geom_line(linewidth = 0.8) +
  
  scale_x_discrete(breaks = c(500, 1e3, 1e4, 1e5)) +

  # geom_errorbar(aes(ymin = mean_brier - sd_brier,
                #     ymax = mean_brier + sd_brier), 
                # width= 0.1) +
  
  scale_color_manual(values = c("True" = "#F8766D",
                                "Full_Data" = "#CD9600", 
                                "Training_Set" = "#00C19A", 
                                "Test_Set" = "#00A9FF",
                                "Nuisance_Set" = "#ED68ED")) + 

  
  scale_shape_manual(values = c("True" = 8,
                                "Full_Data" = 15,
                                "Training_Set" = 16,
                                "Test_Set" = 17,
                                "Nuisance_Set" = 18)) +

  scale_linetype_manual(values = c( "True" = "solid",
                                    "Full_Data" = "dashed",
                                   "Training_Set" = "dotted",
                                   "Test_Set" = "dotdash",
                                   "Nuisance_Set" = "longdash")) +
  
  guides(color = guide_legend("Strategy"), shape = guide_legend("Strategy"), linetype = "none") +
  
  scale_y_continuous(limits = c(0.17, 0.4)) +


  labs(x = "Sample Size", y = "Mean Brier Score") +
       #title = "Average Brier Score (A=0)") 
  
  theme_minimal()

# ggsave("mean_briers0_gam.png", plot = mean_briers0_gam)


```

### Overall Performance Measures
Here we compute the bias, variance and RMSE related to the Brier score estimates.
```{r performance measures}
# extract the true values per sample size
true_values <- summary_A0 %>% filter(strategy == "True") %>%
  dplyr::select(sample_size, true_brier = mean_brier)

# join true values to all rows
# compute bias, variance, and RMSE
sum_all_A0 <- summary_A0 %>%
  left_join(true_values, by = "sample_size") %>%
  filter(strategy != "True") %>%
  mutate(bias = mean_brier - true_brier,
         variance = sd_brier^2,
         rmse = sqrt(bias^2 + variance)) %>%
  mutate(strategy = factor(strategy, 
                           levels = c("Full_Data", "Training_Set", 
                                      "Test_Set", "Nuisance_Set")))

# select relevant columns
table_GAM_A0 <- sum_all_A0 %>%
  select(sample_size, strategy, bias, variance, rmse)


# plots for bias, variance, and RMSE

# ggplot(data = sum_all_A0,
#        aes(x = as.factor(sample_size),
#            y = bias,
#            color = strategy,
#            shape = strategy,
#            linetype = strategy,
#            group = strategy)) +
# 
#   geom_point(size = 3) +
#   geom_line(linewidth = 0.8) +
#   scale_y_continuous(limits = c(-0.0001, 0.05))
# 
# 
# ggplot(data = sum_all_A0,
#        aes(x = as.factor(sample_size),
#            y = variance,
#            color = strategy,
#            shape = strategy,
#            linetype = strategy,
#            group = strategy)) +
# 
#   geom_point(size = 3) +
#   geom_line(linewidth = 0.8) +
#   scale_y_continuous(limits = c(-0.0001, 0.0005))
# 
# ggplot(data = sum_all_A0,
#        aes(x = as.factor(sample_size),
#            y = rmse,
#            color = strategy,
#            shape = strategy,
#            linetype = strategy,
#            group = strategy)) +
# 
#   geom_point(size = 3) +
#   geom_line(linewidth = 0.8) +
#   scale_y_continuous(limits = c(-0.0001, 0.05))

```



## Treated Group
Performing same as above, but with the treatment group (a=1).
### Distribution of Brier scores
```{r}
# transform into long format 
long_df1_gam <- combined_results_gam %>%
  dplyr::select(replication, sample_size, True_A1, Est1_A1, Est2_A1, Est3_A1, Est4_A1) %>%
  tidyr::pivot_longer(cols = starts_with("True_A1"):starts_with("Est4_A1"), 
               names_to = "strategy", values_to = "brier_score")

long_df1_gam <- long_df1_gam %>% mutate(strategy = recode(strategy,
                           "True_A1" = "True",
                           "Est1_A1" = "Full_Data",
                           "Est2_A1" = "Training_Set",
                           "Est3_A1" = "Test_Set",
                           "Est4_A1" = "Nuisance_Set")) %>%
            mutate(strategy = factor(strategy, 
                           levels = c("True","Full_Data", 
                                      "Training_Set", "Test_Set", 
                                      "Nuisance_Set")))

#-------------------------------------------------------------------------------

# Boxplot: distribution of average estimates from 100 replications
boxplot1_gam <- ggplot(long_df1_gam, 
                      aes(x = strategy, y = brier_score, 
                          fill = strategy, color = strategy)) +
  
  geom_jitter(alpha = 0.5) +
  geom_boxplot(alpha = 0.7, color = "black") +
  
  labs(# title = "Distribution of Brier Scores (A=1)",
       # subtitle = "Logistic Regression Nuisance Model", 
       # caption = "Average estimates from 1000 replications",
       y = "Average Brier Score", x = "") +
  
  scale_color_manual(values = c("True" = "#F8766D",
                                "Full_Data" = "#CD9600", 
                                "Training_Set" = "#00C19A", 
                                "Test_Set" = "#00A9FF",
                                "Nuisance_Set" = "#ED68ED"), 
                     name = "Strategy") +
  
  scale_fill_manual(values = c("True" = "#F8766D",
                                "Full_Data" = "#CD9600", 
                                "Training_Set" = "#00C19A", 
                                "Test_Set" = "#00A9FF",
                                "Nuisance_Set" = "#ED68ED"), 
                    name = "Strategy") +

  theme_minimal() +
  
  theme(axis.text.x = element_blank()) +
  
  facet_wrap(~sample_size) +
  
  scale_y_continuous(limits = c(0.16, 0.26)) 


# ggsave("boxplot1_gam.png", plot = boxplot1_gam)
```


### Average Scores
```{r}
results_A1 <- combined_results_gam %>% dplyr::select(replication, sample_size, 
                                 True_A1, Est1_A1, Est2_A1, Est3_A1, Est4_A1)

summary_stats_A1 <- results_A1 %>%
  group_by(sample_size) %>%
  summarise(across(.cols = c(True_A1, Est1_A1, Est2_A1, Est3_A1, Est4_A1),
                   .fns = list(mean_brier = mean, sd_brier = sd),
                   .names = "{.col}_{.fn}"))

summary_A1 <- summary_stats_A1 %>%
  tidyr::pivot_longer(
    cols = -sample_size, 
    names_to = c("strategy", "metric"), 
    names_sep = "_A1_") %>%
  tidyr::pivot_wider(names_from = metric,
                     values_from = value) %>%
  mutate(strategy = recode(strategy,
                           "True" = "True",
                           "Est1" = "Full_Data",
                           "Est2" = "Training_Set",
                           "Est3" = "Test_Set",
                           "Est4" = "Nuisance_Set")) %>%
  mutate(strategy = factor(strategy, 
                           levels = c("True","Full_Data", 
                                      "Training_Set", "Test_Set", 
                                      "Nuisance_Set")))
```


```{r}
mean_briers1_gam <- ggplot(data = summary_A1, 
       mapping = aes(x = as.factor(sample_size),
                     y = mean_brier, 
                     color = strategy, 
                     shape = strategy, 
                     linetype = strategy, 
                     group = strategy)) +
  
  geom_point(size = 3) +
  geom_line(linewidth = 0.8) +
  
  scale_x_discrete(breaks = c(500, 1e3, 1e4, 1e5)) +

  # geom_errorbar(aes(ymin = mean_brier - sd_brier,
                #     ymax = mean_brier + sd_brier), 
                # width= 0.1) +
  
  scale_color_manual(values = c("True" = "#F8766D",
                                "Full_Data" = "#CD9600", 
                                "Training_Set" = "#00C19A", 
                                "Test_Set" = "#00A9FF",
                                "Nuisance_Set" = "#ED68ED")) + 

  
  scale_shape_manual(values = c("True" = 8,
                                "Full_Data" = 15,
                                "Training_Set" = 16,
                                "Test_Set" = 17,
                                "Nuisance_Set" = 18)) +

  scale_linetype_manual(values = c( "True" = "solid",
                                    "Full_Data" = "dashed",
                                   "Training_Set" = "dotted",
                                   "Test_Set" = "dotdash",
                                   "Nuisance_Set" = "longdash")) +
  
  guides(color = guide_legend("Strategy"), shape = guide_legend("Strategy"), linetype = "none") +
  

  labs(x = "Sample Size", y = "Mean Brier Score") + 
       # title = "Average Brier Score (A=1)") +
  
  scale_y_continuous(limits = c(0.17, 0.20)) +
  
  theme_minimal()


# ggsave("mean_briers1_gam.png", plot = mean_briers1_gam)

```


### Overall Performance Measures
#### Bias, Variance, RMSE
```{r}
# extract the true values per sample size
true_values <- summary_A1 %>% filter(strategy == "True") %>%
  dplyr::select(sample_size, true_brier = mean_brier)

# join true values to all rows
sum_all_A1 <- summary_A1 %>%
  left_join(true_values, by = "sample_size") %>%
  filter(strategy != "True") %>%
  mutate(bias = mean_brier - true_brier,
         variance = sd_brier^2,
         rmse = sqrt(bias^2 + variance)) %>%
  mutate(strategy = factor(strategy, 
                           levels = c("Full_Data", "Training_Set", 
                                      "Test_Set", "Nuisance_Set")))

# select relevant columns
table_GAM_A1 <- sum_all_A1 %>%
  select(sample_size, strategy, bias, variance, rmse)
```


